How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-06 research/paper/draft.tex

Finally we may return to Eq. \ref{eq:hyperbayes} to express the log-hyperposterior $\ln\left[p(\vec{\theta}|\{\vec{d}_{i}\})\right]$ in terms of the photo-$z$ interim posteriors $\{p(z_{i}|\vec{d}_{i}, \vec{\theta}^{*})\}$, as in Eq. \ref{eq:final}.
\begin{align}
\label{eq:final}
\ln\left[p(\vec{\theta}|\{\vec{d}_{i}\})\right] &\propto \ln\left[p(\vec{\theta})\right] + \sum_{i}\ln\left[\int\ p(z_{i}|\vec{d}_{i}, \vec{\theta}^{*})\ \frac{p(z_{i}|\vec{\theta})}{p(z_{i}|\vec{\theta}^{*})}\ dz_{i}\right]
\end{align}
Now we have an expression for a quantity proportional to the log-hyperposterior we desire!  Though the constant of proportionality, $p(\{\vec{d}_{i}\})$ is in general not possible to calculate, we may still characterize the log-hyperposterior by way of MCMC sampling.

@@

\subsection{Model Specifics}
\label{sec:choices}

@@

>>>>

Finally we may return to Eq. \ref{eq:hyperbayes} to express the log-hyperposterior $\ln\left[p(\vec{\theta}|\{\vec{d}_{i}\})\right]$ in terms of the photo-$z$ interim posteriors $\{p(z_{i}|\vec{d}_{i}, \vec{\theta}^{*})\}$, as in Eq. \ref{eq:final}.
\begin{align}
\label{eq:final}
\ln\left[p(\vec{\theta}|\{\vec{d}_{i}\})\right] &\propto \ln\left[p(\vec{\theta})\right] + \sum_{i}\ln\left[\int\ p(z_{i}|\vec{d}_{i}, \vec{\theta}^{*})\ \frac{p(z_{i}|\vec{\theta})}{p(z_{i}|\vec{\theta}^{*})}\ dz_{i}\right]
\end{align}
Now we have an expression for a quantity proportional to the log-hyperposterior we desire!  Though the constant of proportionality, $p(\{\vec{d}_{i}\})$ is in general not possible to calculate, we may still characterize the log-hyperposterior by way of MCMC sampling and optimization, which will be discussed in Sec. \ref{sec:implementation}.

@@

@@

This method is presented in contrast to existing methods for inferring $n(z)$ from photo-$z$ PDFs, which fall into two broad categories: stacking and point estimation.  Stacking assumes Eq. \ref{eq:stacking}, where the constant of proportionality is chosen to ensure $\int f_{\vec{\theta}}(z)\ dz$ is unity.
\begin{align}
\label{eq:stacking}
f_{\vec{\theta}}(z) &\propto \sum_{i}p(z_{i}|\vec{d}_{i}, \vec{\theta}^{*})
\end{align}

\section{Implementation}
\label{sec:implementation}

We introduce the Cosmological Hierarchical Inference with Probabilistic Photometric Redshifts (CHIPPR) code as a comprehensive package for estimating $n(z)$ from catalogs of photo-$z$ PDFs.  In particular, CHIPPR implements both sampling and optimization of Eq. \ref{eq:final} and compares the results to those of the more traditional approaches presented in Sec. \ref{sec:alternatives}.
